---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)

set.seed(1992)
library(soccercolleagues)
```

# {soccercolleagues}

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there
has not yet been a stable, usable release suitable for the
public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![R-CMD-check](https://github.com/matt-dray/soccercolleagues/workflows/R-CMD-check/badge.svg)](https://github.com/matt-dray/soccercolleagues/actions)
<!-- badges: end -->

A work-in-progress, proof-of-concept R package to help you find:

* past and present team mates of a named footballer
* a single team mate shared by multiple players at some point

This package is dependent on [the excellent {worldfootballR} package by Jason Zivkovic](https://jaseziv.github.io/worldfootballR/), which helps fetch player data from [Transfermarkt](https://www.transfermarkt.com/).

[Insert gif of Kieran Dyer and Lee Bowyer fighting as Newcastle team mates]

You can install the package from GitHub.

```{r install, eval=FALSE}
remotes::install_github("matt-dray/soccercolleagues")
library(soccercolleagues)
```

Example: fetch all players from all seasons of the English Premier League. This will take several minutes.

```{r get-players}
epl_players <- get_players(
  seasons = 1992:2020,
  country = "England"
)

sample_n(epl_players, 5) |> 
  select(player_name, team_name, season)
```
```
## # A tibble: 5 × 3
##   player_name      team_name           season
##   <chr>            <chr>               <chr> 
## 1 Rob Lee          newcastle-united    1998  
## 2 Gordon Durie     tottenham-hotspur   1992  
## 3 Cheikhou Kouyaté west-ham-united     2017  
## 4 Daniel James     swansea-city        2016  
## 5 Julian Watts     sheffield-wednesday 1995  
```

Sample from all the current and former team mates of a named player. Sampling is weighted by total playing time, so well-known players are more likely to arise.

```{r one-player}
sample_colleagues(
  all_players = epl_players,
  players = "Emile Heskey",
  n = 5
)
```
```
## [1] "Shay Given"    "Dwight Yorke"    "El-Hadji Diouf"
## [4] "Matthew Upson" "Leighton Baines"
```

You can also sample common team mates for a set of named players, if they have any. This is especially sayisfying if they only have one player in common.

```{r answer}
sample_colleagues(
  all_players = epl_players,
  players = c(
    "Shay Given",
    "Dwight Yorke",
    "El-Hadji Diouf",
    "Matthew Upson",
    "Leighton Baines"
  )
)
```
```
## [1] "Emile Heskey"
```

In the spirit of the 'pub quiz' nature of this, there's also an _extremely_ proof-of-concept Shiny app available with `open_colleagues_quiz()`. You'll need to install {shiny} and {shinyjs} from CRAN before you use it.
