---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)

set.seed(1992)
library(soccercolleagues)
```

# {soccercolleagues}

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there
has not yet been a stable, usable release suitable for the
public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->

A work-in-progress, proof-of-concept R package to help you find the past and current team mates of a named footballer, or to find a team mate shared by multiple players at some point. Inspired by pub-quiz questions in this style.

This package is dependent on [the excellent {worldfootballR} package by Jason Zivkovic](https://jaseziv.github.io/worldfootballR/), which helps fetch player data from [Transfermarkt](https://www.transfermarkt.com/).

[Insert gif of Kieran Dyer and Lee Bowyer fighting as Newcastle team mates]

Install from GitHub.

```{r install, eval=FALSE}
remotes::install_github("matt-dray/soccercolleagues")
library(soccercolleagues)
```

Fetch all players from all seasons of the English Premier League.

```{r get-players}
epl_players <- get_players(
  years = 1992:2020,
  country = "England"
)
```

Find all the team mates of a named player for these years.

```{r one-player}
colleagues <- get_player_colleagues(
  all_players = epl_players,
  player = "James Milner"
)
```

Find a common team mate for a set of named players.

```{r multiple-players}
sample_colleagues(
  all_players = epl_players,
  players = colleagues
)
```

